Empirical Bayes analysis for detection of gene heterosis in RNAseq data

### 2014-12-17 ebayes_rnaseq_heterosis.tex
added bioconductor ref

To begin, we applied the {\tt edgeR} package from Bioconductor (citation needed) to the maize data to obtain sample-specific normalization factors, then gene-specific dispersions, and finally gene-variety-specific location parameters. We treated these parameters as the truth for the simulation study: i.e. a gene with $\mu_{g3} < \min(\mu_{g1}, \mu_{g2})$ was considered to have LPH, while a gene with $\max(\mu_{g1},\mu_{g2}) < \mu_{g3}$ was considered to have HPH. This technique ensured that our simulated datasets maintained the existing covariance structure among the gene-variety means of the original maize data.

>>>>

To begin, we applied the {\tt edgeR} package \citep{robinson2010edgeR} from Bioconductor \citep{gentleman2004bioconductor} to the maize data to obtain sample-specific normalization factors, then gene-specific dispersions, and finally gene-variety-specific location parameters. We treated these parameters as the truth for the simulation study: i.e. a gene with $\mu_{g3} < \min(\mu_{g1}, \mu_{g2})$ was considered to have LPH, while a gene with $\max(\mu_{g1},\mu_{g2}) < \mu_{g3}$ was considered to have HPH. This technique ensured that our simulated datasets maintained the existing covariance structure among the gene-variety means of the original maize data.
